Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-21 awipev-CO2.Rmd
changed calculations of mean voltINT, voltEXT and TseaF

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  )
d_all <- d_hour #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(month = month(month(datetime))) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE))
#restore datetime and date which are mangled by the murtates above
d_all$datetime <- d_hour$datetime
d_all$date <- d_hour$date
```

@@

mean_voltINT_4h <- d_all %>%

@@

  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)

@@

mean_voltEXT_4h <- d_all %>%

@@

  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)

@@

mean_TseaF_4h <- d_all %>%

@@

  ) %>%
  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)

@@

# Periode 2, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all %>%
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
    datetime == as.POSIXct("2017-09-28 13:00:00"),
mean_voltEXT_4h <- d_all %>%
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
    datetime == as.POSIXct("2017-09-28 13:00:00"),
# period 03, mean of 4 previous hours for volt int + volt ext
mean_voltINT_4h <- d_all %>%
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
    datetime == as.POSIXct("2019-09-13 08:00:00"),
mean_voltEXT_4h <- d_all %>%
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
    datetime == as.POSIXct("2019-09-13 08:00:00"),
# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
mean_voltINT_4h <- d_all %>%
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
    datetime == as.POSIXct("2019-09-13 13:00:00"),
mean_voltEXT_4h <- d_all %>%
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
    datetime == as.POSIXct("2019-09-13 13:00:00"),
mean_TseaF_4h <- d_all %>%
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  ) %>%
  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
    datetime == as.POSIXct("2019-09-13 13:00:00"),

>>>>

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  )
d_all <- d_hour #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE))
#restore datetime, date which are mangled by the murtates above
d_all$datetime <- d_hour$datetime
d_all$date <- d_hour$date
d_all$month <- month(d_all$datetime)
```

@@

# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%

@@

  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)

@@

# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%

@@

  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)

@@

# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%

@@

  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)

@@

# Periode 2, mean of 4 next hours for volt int + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
#       datetime <= as.POSIXct("2017-09-28 18:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
#       datetime <= as.POSIXct("2017-09-28 18:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))

# period 03, mean of 4 previous hours for volt int + volt ext
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
#       datetime <= as.POSIXct("2019-09-13 07:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)

# Ce qui suit (7 lignes) est très bizarre
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# ???????? mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
#       datetime <= as.POSIXct("2019-09-13 07:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))

# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
#       datetime <= as.POSIXct("2019-09-13 12:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
#       datetime <= as.POSIXct("2019-09-13 12:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
#       datetime <= as.POSIXct("2019-09-13 12:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))
